\documentclass[a4paper,11pt]{article}
\usepackage{amsmath}
\usepackage[margin=2.4cm]{geometry}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{COMP30024 Project Part A Report}
\rhead{Alexander Westcott \& Cameron Chandler}
\setlength{\headheight}{14pt}

\author{Alexander Westcott 994344 \& Cameron Chandler 993990}
\title{COMP30024 Artificial Intelligence Project Part B Report}
\date{May 2020}

\begin{document}
\maketitle

% Top marks on spec:

% Work that demonstrates a highly successful application of important techniques discussed
% in class for playing adversarial games, along with many significant theoretical, strategic, or algorithmic
% enhancements to those techniques, based on independent research into algorithmic game-playing or
% original strategic insights into the game being played, leading to a program with excellent performance.




\section{Action Selection}
Describe the approach your game-playing program uses for deciding on which actions to take throughout
the game. Comment on your choice of search algorithm, and on any modifications you have made, and
why. Explain your evaluation function and its features, including their strategic motivations.

\section{Machine Learning}
If you have applied machine learning, discuss how it fits into your program’s overall game-playing approach,
and discuss the learning methodology you followed for training and why you followed this methodology.
Discuss treestrap here, or below? 

\section{Overall Effectiveness}
Comment on the overall effectiveness of your game-playing program. If you have created multiple game-
playing programs using different techniques, compare their relative effectiveness, and explain how you chose
which program to submit for performance assessment.


\section{Additional Areas of Note}
Include a discussion of any other important creative or technical aspects of your work, such as: algorithmic
optimisations, specialised data structures, any other significant efficiency optimisations, alternative or en-
hanced algorithms beyond those discussed in class, other significant ideas you have incorporated from your
independent research, and any supporting work you have completed to assist in the process of developing
an Expendibots-playing program.

\subsection{Move ordering}

\subsection{Opening book}

\subsection{Endgame}

\subsection{Memoisation}
Made sense during training, not for final player


\subsection{Zobrist Hashing}



\end{document}